Untitled

### 2025-03-14 script/r/discontinuity_plot.Rmd
maj

```{r}
ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
  # Add vertical line at border
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", size = 0.8) +

@@

  # Format axes
  scale_x_continuous(labels = function(x) x / 1000,
                    breaks = seq(-40000, 40000, 10000)) +

  # Add clear labels
  labs(x = "Distance from the Border (in km)",
      y = "Political Trust") +
      #title = "Border Discontinuity in Political Trust",
      #subtitle = "Comparing areas close to vs. far from the capital") +

  # Polish theme
  theme_minimal()+
  theme(
  text = element_text(family = "Arial"),
    plot.title = element_text(size = 25, hjust = 0.5, face = "bold", margin = margin(b = 10)), 
    plot.subtitle = element_text(size = 20, hjust = 0.5, margin = margin(b = 20)),
    axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 30)),
    axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 30)),
    axis.text = element_text(size = 11),
    legend.position = c(0.85, 0.2),
    legend.background = element_rect(fill = alpha('white'), color = "gray80"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 20),
    panel.grid.major = element_line(color = "gray90"),
    panel.grid.minor = element_blank(),
    plot.margin = margin(t = 20, r = 20, b = 20, l = 20)
  )

ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity2.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
```

>>>>

```{r}
ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
  # Add vertical line at border
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", size = 0.7) +

@@

  # Format axes
scale_x_continuous(labels = function(x) abs(x) / 1000,
                     breaks = seq(-40000, 40000, 10000)) +  
  # Add clear labels
  labs(x = "Distance from the Border (in km)",
      y = "Political Trust") +

  # Polish theme
theme_minimal() +
  theme(
    text = element_text(family = "Arial"),
    plot.title = element_text(size = 25, hjust = 0.5, face = "bold", margin = margin(b = 10)),
    plot.subtitle = element_text(size = 20, hjust = 0.5, margin = margin(b = 20)),
    axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 25)),
    axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 25)),
    axis.text = element_text(size = 11),
    axis.ticks = element_line(color = "black"),  # Keep the ticks
    axis.ticks.length = unit(5, "pt"),  # Adjust the length of the ticks if needed
    axis.line = element_line(color = "black"),  # Ensure the axis lines are visible
    legend.position = c(0.85, 0.2),
    legend.background = element_rect(fill = alpha('white'), color = "gray80"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 20),
    panel.grid.major.x = element_blank(),  # Remove vertical major grid lines
    panel.grid.minor.x = element_blank(),  # Remove vertical minor grid lines
    panel.grid.major.y = element_line(color = "gray90"),  # Keep horizontal major grid lines
    panel.grid.minor.y = element_blank(),  # Remove horizontal minor grid lines
    plot.margin = margin(t = 20, r = 20, b = 18, l = 18)
  )

ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
```
